Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.8)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-01 experiment_and_data.tex
updates of experiment and data selection section

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35, $W^{2}$ $>$
9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
rest frame. The polar angle between the virtual and real photons was required to
be within the limits 5 mrad $<$
$\theta_{\gamma^{*}\gamma}$ $<$ 45 mrad.

An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon, $p$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

>>>>

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details.

An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.
The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35, $W^{2}$ $>$
9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
rest frame. The polar angle between the virtual and real photons was required to
be within the limits 5 mrad $<$
$\theta_{\gamma^{*}\gamma}$ $<$ 45 mrad.

An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.
